{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-11-30 thesis/overview.tex
relaxed memory in glossary and other overview todos

% TODO: Talk about the hurdle (both for p2 and p3).

@@

Although there is some variety in supplemental assignments, all Pintos courses include three core projects building on the Pintos basecode:
\begin{itemize}
	\item {\em Threads}: Students must implement an ``alarm clock'' (analogous to Pebbles's {\tt sleep} system call),
		a priority scheduling algorithm, and a multi-level feedback queue scheduler.
		% TODO: Later. Talk about how concurrency testing can only test certain parts of this crap.
	\item {\em Userprog}: Provided with rudimentary virtual memory and ELF loader implementations, students must implement argument passing and several system calls associated with userspace programs, including {\tt exec}, {\tt exit}, {\tt wait}, and file descriptor management.
	\item {\em Filesys}: Provided with a simple ``flat'' filesystem implementation, students must extend it with a buffer cache, extensible files, and subdirectories.
\end{itemize}

@@

		which may result in bugs by being reordered by the compiler or hardware;
		% TODO: put a section reference for weak memory
		% mb have to write a section on it here
		however, this thesis checks programs at the executable level and assumes sequential consistency,

@@

@@

@@

		\footnote{In the author's personal experience, readers of their M.S. thesis \cite{landslide}

@@

@@

@@

@@

>>>>

% haha-never: Talk about the hurdle (both for p2 and p3).

@@

Although there is some variety in supplemental assignments, all Pintos courses include three core projects building on the Pintos basecode:
\begin{itemize}
	\item {\em Threads}: Students must implement an ``alarm clock'' (analogous to Pebbles's {\tt sleep} system call),
		a priority scheduling algorithm, and a multi-level feedback queue scheduler.
		% haha-never: Later. Talk about how concurrency testing can only test certain parts of this crap.
	\item {\em Userprog}: Provided with rudimentary virtual memory and ELF loader implementations, students must implement argument passing and several system calls associated with userspace programs, including {\tt exec}, {\tt exit}, {\tt wait}, and file descriptor management.
	\item {\em Filesys}: Provided with a simple ``flat'' filesystem implementation, students must extend it with a buffer cache, extensible files, and subdirectories.
\end{itemize}

@@

		which may result in bugs by being reordered by the compiler or hardware (see {\em relaxed memory});
		however, this thesis checks programs at the executable level and assumes {\em sequential consistency},

@@

	\item \revision{{\bf Partial store order.} See {\em relaxed memory.}}

@@

	\item \revision{{\bf PSO.} {\em Partial store order}. See {\em relaxed memory}.}

@@

		\footnote{In the author's personal experience, many readers of their M.S. thesis \cite{landslide}

@@

	\item \revision{{\bf Relaxed memory.}
		Also known as {\em weak memory}.
		A family of multiprocessor execution semantics
		that allows reads and/or writes of shared memory to become visible to different CPUs in different sequences.
		Under {\em total store order} (TSO),
		implemented for example on x86,
		one CPU's writes may appear reordered after its subsequent loads, from the perspective of another CPU.
		Under {\em partial store order} (PSO),
		either writes and/or reads may appear reordered after other subsequent writes and/or reads.
		On ARM's implementation of PSO, all such combinations are possible.
		Safe concurrent programming on such architectures requires careful use
		of acquire and/or release memory barriers
		\cite{sully-thesis}.
		By contrast, {\em sequential consistency} (SC) permits no such reorderings.
		% TODO: check that quicksand discussion shouldn't perhaps get a more subsection'ed sect reference
		For further discussion see \sect{\ref{sec:quicksand-discussion}} and \sect{\ref{sec:tm-warpzone-relaxed}}.}

@@

	\item {\bf Sequential consistency.} See {\em relaxed memory}.

@@

	\item \revision{{\bf Total store order.} See {\em relaxed memory.}}
	\item \revision{{\bf TSO.} {\em Total store order}. See {\em relaxed memory.}}

@@

	\item \revision{{\bf Weak memory.}
		See {\em relaxed memory.}}
